---
title: "Beer & Brewery Report"
author: "Quentin, Sita, Olha, Tosin"
date: "2/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Case Study 1

## Questions

### How many breweries are present in each state?





###  Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.







### Report the number of `NA's` In each column.






### Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.







### Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?







### Summary statistics for the ABV variable.








### Is there an apparent relationship between the bitterness of the beer and its alcoholic content?

In order for us to better examine whether or not there is a relationship betwen the bitterness of the beer and its alcoholic content we will take a look at
the `ABV` and `IBU` data. The `ABV` data represents our alchol volumn measurement within the beer itself, and the `IBU` represents the international bitterness
measurement of the beer. Before we can plot these we must create a subset of this data set.

```{r}

#Import the file
beers <- read.csv('data/Beers.csv')

#create a subset for the variables ABV and IBU as they are our variables fo interest
bitter_vs_alc <- subset(beers, subset = is.na(IBU) == FALSE, select = c(ABV, IBU))

head(bitter_vs_alc)
```


Now that we have prepared our data we will plot it to better understand the relationship.

```{r}
library(ggplot2)

ggplot(data=bitter_vs_alc, aes(x=ABV, y=IBU)) +
  geom_point(pch = 20, color = "brown", size=2) +
  geom_smooth(method="lm", color="red", linetype=2) +
  labs(title="Alcoholic Content vs Bitterness",
       x="Alcohol by Volume", y="International Bitterness Units")
```


Based on our chart above we can conclude that there is a positive relationship between the alchol content and bitterness units based on our line present through the graph. We can also see that as bitterness increases we also expect to see an increase in the alchol levles. This suggests that if a beer has a bitter taste, the alchol content could be high for that specific beer.
